Efficiently stable presentations from error-correcting codes

### 2023-07-12 efficient_stability.tex
edits to correct the comment about unitaries

For $u\in \F_q^m$ let $\{P^{u}_\beta\}_{\beta \in \F_q}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}, and 
\[ U_u = \sum_{\beta\in\F_q} \omega_q^\beta P^u_{\beta}\;,\]
where $\omega_q = e^{2i\pi/q}$. (\tnote{added:}To define $\omega_q^\beta$ for $\beta\in \F_q$, we use the representative of $\beta$ in $\{0,\ldots,q-1\}$.)
Then $U_u \in \mU(\mM)$.

@@

\begin{claim}\label{claim:z2-stab-2b}
For $u\in \F_q^m$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i} = U_{u+ie_j}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ and $j$ implicit). Then 
\begin{equation}\label{eq:z2-stab-2b-0a}
\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\}\\i\neq i' \in \{0,\ldots,d\}}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_i^\alpha, U_{i'}^{\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;, 
\end{equation}
and
\begin{equation}\label{eq:z2-stab-2b-0b}
 \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_u^\alpha, U_{v}^{\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
\end{equation}
where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$, and $[U,V]=UVU^\dagger V^\dagger$ is the group commutator. 
\hnote{should we clarify what it means to raise a unitary to a power in a finite field? I assume there's some canonical identification of elements of $\F_q$ with $\{0,1,2,\ldots,q-1\}$?}\tnote{I got confused by this. I added a comment above. What we need is that $(\omega_q^\alpha)^\beta = \omega_q^{\alpha \beta}$, for the field multiplication $\alpha \beta$. This will not be satisfied by an arbitrary choice of representative, right?} \hnote{Yeah I'm not sure this works... the multiplication over $\F_q$ for $q = 2^t$ does not look like multiplication in $\Z_q$; it's some more complicated linear transformation that has to do with irreducible polynomials and stuff...} \hnote{why do we need to package everything into a unitary, though? The low degree test/tensor codes stuff only needs line/points measurements}
\end{claim}

\begin{proof}
Due to the test of the relations $\{R^\com_k\}$, it holds that 
\begin{align}
\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{\alpha,\beta\in \F_q} \big\| [\phi(s_{u+i e_j,\alpha}),\phi(s_{u+i' e_j,\beta})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
\Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| [\phi(s_{u,\alpha}),\phi(s_{v,\beta})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}
\end{align}
Now, for any $u,v\in \F_q^m$
\begin{align*}
\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_u^\alpha U_{v}^{\alpha'} U_u^{-\alpha} U_{v}^{-\alpha'} \big) \\
&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')} \Es{\alpha'\in \F_q} \omega_q^{\alpha'(\gamma-\gamma')}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot\kappa(\beta-\beta')} \Es{\alpha'\in\F_2^t} (-1)^{\alpha'\cdot\kappa(\gamma-\gamma')} \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\Es{\alpha,\alpha'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_q} (-1)^{\alpha\cdot \kappa(\beta)} P^{u}_\beta\Big) \Big(\sum_{\gamma\in \F_q} (-1)^{\alpha'\cdot \kappa(\gamma)} P^{v}_\gamma\Big)\Big(\sum_{\beta'\in \F_q} (-1)^{\alpha\cdot \kappa(\beta')} P^{u}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_q} (-1)^{\alpha'\cdot \kappa(\gamma')} P^{v}_{\gamma'}\Big)\Big)\;.
\end{align*}
Here, the second line follows since for $\beta,\beta'\in \F_q$, 
\[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
\begin{align*}
\Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_u^\alpha ,U_{v}^{\alpha'} ]-\Id\big\|_\tau^2
&= \Es{\alpha,\alpha'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{\alpha\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_2^t} (-1)^{\alpha\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
&= \Es{\alpha,\alpha'\in \F_2^t} \big\| \big[ \phi(s_{u,\alpha}),\phi(s_{v,\alpha'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
\end{align*}
where the second line follows from Claim~\ref{claim:z2-stab-2}. Thus~\eqref{eq:z2-stab-2b-0a} follows from~\eqref{eq:z2-stab-2b-1}, and~\eqref{eq:z2-stab-2b-0b} follows from~\eqref{eq:z2-stab-2b-1b}.
\end{proof}

@@

\begin{claim}\label{claim:z2-stab-3}
For every $u\in \F_q^m$ and $j\in\{1,\ldots,m\}$, there is a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in\F_q^{d+1}}$ on $\mM$ such that 
\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{z_0,\ldots,z_{d}\in \F_q} \Big\| U_0^{z_0}\cdots U_d^{z_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
Similarly, for any $u,v\in \F_q^m$ there is a projective measurement $\{R^{u,v}_{\alpha,\beta}\}_{(\alpha,\beta)\in\F_q^{2}}$ on $\mM$ such that 
\[  \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}} \Es{y,z\in \F_q} \Big\| U_u^{z}  U_v^{y} -  \sum_{\alpha} \omega^{ \alpha z + \beta y} R^{u,v}_{\alpha,\beta}\Big\|_\tau^2 \,=\, \poly(\eps)\;.\]
\end{claim}

\begin{proof}
We show the first part only, as the second part is entirely analogous. Fix an $u\in \F_q^m$ and a direction $j\in \{1,\ldots,m\}$. Define
$\psi: \Z_q^{d+1} \to \mU(\mM)$ by 
\[\psi(z_0,\ldots,z_{d}) \,=\, U_0^{z_0} \cdots U_{d}^{z_{d}}\;,\]
where for each $i\in\{0,\ldots,d\}$, $U_i$ is the order-$q$ unitary defined in Claim~\ref{claim:z2-stab-2b}. Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_q^{d+1}$ on $\mU(\mA)$, with respect to the exhaustive presentation. To verify this first note that for any unitaries $V,W$, and any $i,i'$ we have that on average over $u$ and $j$,
\begin{align*}
\Es{\alpha,\alpha'\in \F_q} \big\| V U_i^\alpha U_{i'}^{\alpha'} W^* - V U_{i'}^{\alpha'} U_i^\alpha  W^*\big\|_\tau^2 \,=\, O\big(d^2 \sqrt{\eps}\big)\;,
\end{align*}
by Claim~\ref{claim:z2-stab-2b}, where the factor $d^2$ is because we require the relation to hold for all $i,i'$. Applying this relation $O(d^2)$ times gives
\begin{align*}
 \Es{z_0,\ldots,z_d\in\F_q}\Es{y_0,\ldots,y_d\in\F_q}\big\|\psi(z_0,\ldots,z_d)\psi(y_0,\ldots,y_d) -\psi(z_0+y_0,\ldots,z_d+y_d)\big\|_\tau^2 \,=\, O\big(d^4 \sqrt{\eps}\big)\;,
\end{align*}
as desired.
Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_i\}$ of order $q$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$,
\begin{equation}\label{eq:z2-stab-3-1}
\Es{z_0,\ldots,z_{d}\in\F_q} \big\| \psi(z_0,\ldots,z_{d+1}) - w^* V_0^{z_0}\cdots V_{d}^{z_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
\end{equation}
Because $\{V_i\}$ are a representation of $\Z_q^{d+1}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \F_q^{d+1}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$, 
\[ V_i \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\alpha_i} Q_\alpha\;,\]
and  
\[ V_0^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum z_i\alpha_i} Q_\alpha\;.\]
%($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in \Z_q^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum z_i\alpha_i} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
\end{proof}

@@

\begin{claim}\label{claim:z2-stab-5}
Use the same notation as in Claim~\ref{claim:z2-stab-2b}. Let $u\in \F_q^m$, $\ell$ an axis-parallel line through $u$ and $v\in\F_q^m\cap \ell$. Let $(\alpha_{u,v,i})_{i=0,\ldots,d}$ be the interpolation coefficients~\eqref{eq:interp-coeff}. Let $U_v = \sum_\beta \omega^\beta P^v_\beta$. Then 
\begin{equation}\label{eq:z2-stab-5-0}
\Es{u\in\F_q^m} \Es{\ell: u\in \ell} \Es{v\in \ell} \Es{\gamma\in\F_q} \Big\| U_0^{\gamma \alpha_{u,v,0}}\cdots U_d^{\gamma  \alpha_{u,v,d}} - U_v^\gamma \big\|_\tau^2 \,=\, 1-O\big(d\sqrt{\eps}\big)\;,
\end{equation}
where the expectation is over a uniformly random axis-parallel line that contains $u$, and a uniformly random $v\in\ell$. 
\end{claim}

\begin{proof}
Write $\alpha_i$ for $\alpha_{u,v,i}$. 
We observe that 
\begin{align*}
\Es{\gamma\in\F_q} \tau\big( U_0^{\gamma\alpha_{0}}\cdots U_d^{\gamma\alpha_{d}} U_v^{-\gamma} \big)
&=  \sum_{\beta_0,\ldots,\beta_d\in\F_q}\sum_{\beta\in\F_q} \Es{\gamma\in\F_q} \omega^{\sum \gamma \alpha_i\beta_i} \omega^{-\gamma\beta} \tau\big( P^{(0)}_{\beta_0} \cdots P^{(d)}_{\beta_d} P^v_\beta \big)\\
&= \sum_{\beta_0,\ldots,\beta_d\in\F_q}\sum_{\beta\in\F_q}\Es{\gamma\in\F_2^t} (-1)^{\gamma\cdot \kappa(\sum \alpha_i\beta_i-\beta)} \tau\big( P^{(0)}_{\beta_0} \cdots P^{(d)}_{\beta_d} P^v_\beta \big)\\
&=\Es{\gamma\in\F_2^t}  \tau\Big( \Big(\sum_{\beta_0\in \F_q} (-1)^{\gamma\cdot \kappa(\alpha_0\beta_0)} P^{(0)}_{\beta_0} \Big)\cdots\Big(\sum_{\beta\in \F_q} (-1)^{-\gamma\cdot \kappa(\beta)} P^{v}_{\beta} \Big)\Big)\\
&=\Es{\gamma\in\F_q}  \tau\Big( \Big(\sum_{\beta_0\in \F_q} (-1)^{\kappa( \gamma \alpha_0)\cdot\kappa(\beta_0)} P^{(0)}_{\beta_0} \Big)\cdots\Big(\sum_{\beta\in \F_q} (-1)^{\kappa(-\gamma)\cdot \kappa(\beta)} P^{v}_{\beta} \Big)\Big)\;.
\end{align*}
By repeated application of Claim~\ref{claim:z2-stab-2}, the last expression is within $O(d\sqrt{\eps})$ of 
\[ \Es{\gamma\in\F_q}  \tau\big( \phi(s_{u+ie_j,\kappa(\gamma \alpha_0)})\cdots \phi(s_{v,\kappa(-\gamma)}) \big)\;.\]
The latter expression is a random relation in $R^\ld_k$, and so, on average over $u,j$ and $v$ it is $1-O(\eps)$.
\end{proof}

>>>>

\tnote{changed this, and modified everything downstream}
For $u\in \F_q^m$ let $\{P^{u}_\beta\}_{\beta \in \F_q}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}. For $\alpha\in \F_q$, let  
\[ U_{u,\alpha} = \sum_{\beta\in\F_q} (-1)^{\tr(\alpha\beta)} P^u_{\beta}\;.\]
%where $\omega_q = e^{2i\pi/q}$. (\tnote{added:}To define $\omega_q^\beta$ for $\beta\in \F_q$, we use the representative of $\beta$ in $\{0,\ldots,q-1\}$.)
Then $U_{u,\alpha} \in \mU(\mM)$.

@@

\begin{claim}\label{claim:z2-stab-2b}
For $u\in \F_q^m$, $\alpha\in\F_q$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i,\alpha} = U_{u+ie_j,\alpha}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ and $j$ implicit). Then 
\begin{equation}\label{eq:z2-stab-2b-0a}
\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\}\\i\neq i' \in \{0,\ldots,d\}}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_{i,\alpha}, U_{i',\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;, 
\end{equation}
and
\begin{equation}\label{eq:z2-stab-2b-0b}
 \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_{u,\alpha}, U_{v,\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
\end{equation}
where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$, and $[U,V]=UVU^\dagger V^\dagger$ is the group commutator. 
\hnote{should we clarify what it means to raise a unitary to a power in a finite field? I assume there's some canonical identification of elements of $\F_q$ with $\{0,1,2,\ldots,q-1\}$?}\tnote{I got confused by this. I added a comment above. What we need is that $(\omega_q^\alpha)^\beta = \omega_q^{\alpha \beta}$, for the field multiplication $\alpha \beta$. This will not be satisfied by an arbitrary choice of representative, right?} \hnote{Yeah I'm not sure this works... the multiplication over $\F_q$ for $q = 2^t$ does not look like multiplication in $\Z_q$; it's some more complicated linear transformation that has to do with irreducible polynomials and stuff...} \hnote{why do we need to package everything into a unitary, though? The low degree test/tensor codes stuff only needs line/points measurements}\tnote{The unitary is the best way to make use of the commutation relations; I wasn't able to control the errors without them. I redid it, without $\omega$'s, doing everything as if it was $\Z_2^t$ instead of $\F_q$.}
\end{claim}

\begin{proof}
Due to the test of the relations $\{R^\com_k\}$, it holds that 
\begin{align}
\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{\alpha,\beta\in \F_q} \big\| [\phi(s_{u+i e_j,\alpha}),\phi(s_{u+i' e_j,\beta})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
\Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| [\phi(s_{u,\alpha}),\phi(s_{v,\beta})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}
\end{align}
Now, for any $u,v\in \F_q^m$
\begin{align*}
\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_{u,\alpha} U_{v,\alpha'} U_{u,-\alpha} U_{v,-\alpha'} \big) \\
&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} (-1)^{\tr(\alpha(\beta-\beta'))} \Es{\alpha'\in \F_q} (-1)^{\tr(\alpha'(\gamma-\gamma'))}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{a\in\F_2^t} (-1)^{a\cdot\kappa(\beta-\beta')} \Es{a'\in\F_2^t} (-1)^{a'\cdot\kappa(\gamma-\gamma')} \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
&=\Es{a,a'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta\Big) \Big(\sum_{\gamma\in \F_q} (-1)^{a'\cdot \kappa(\gamma)} P^{v}_\gamma\Big)\Big(\sum_{\beta'\in \F_q} (-1)^{a\cdot \kappa(\beta')} P^{u}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_q} (-1)^{a'\cdot \kappa(\gamma')} P^{v}_{\gamma'}\Big)\Big)\;.
\end{align*}
%Here, the second line follows since for $\beta,\beta'\in \F_q$, 
%\[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
%It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
\begin{align*}
\Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_{u,\alpha} ,U_{v,\alpha'} ]-\Id\big\|_\tau^2
&= \Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
&= \Es{\alpha,\alpha'\in \F_q} \big\| \big[ \phi(s_{u,\alpha}),\phi(s_{v,\alpha'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
\end{align*}
where the second line follows from Claim~\ref{claim:z2-stab-2}. Thus~\eqref{eq:z2-stab-2b-0a} follows from~\eqref{eq:z2-stab-2b-1}, and~\eqref{eq:z2-stab-2b-0b} follows from~\eqref{eq:z2-stab-2b-1b}.
\end{proof}

@@

\begin{claim}\label{claim:z2-stab-3}
For every $u\in \F_q^m$ and $j\in\{1,\ldots,m\}$, there is a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in\F_q^{d+1}}$ on $\mM$ such that 
\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{z_0,\ldots,z_{d}\in \F_q} \Big\| U_{0,z_0}\cdots U_{d,z_d} -  \sum_{\alpha} (-1)^{\tr(\sum z_i\alpha_i)} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
Similarly, for any $u,v\in \F_q^m$ there is a projective measurement $\{R^{u,v}_{\alpha,\beta}\}_{(\alpha,\beta)\in\F_q^{2}}$ on $\mM$ such that 
\[  \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}} \Es{y,z\in \F_q} \Big\| U_{u,z}  U_{v,y} -  \sum_{\alpha} (-1)^{ \tr(\alpha z + \beta y)} R^{u,v}_{\alpha,\beta}\Big\|_\tau^2 \,=\, \poly(\eps)\;.\]
\end{claim}

\begin{proof}
We show the first part only, as the second part is entirely analogous. Fix an $u\in \F_q^m$ and a direction $j\in \{1,\ldots,m\}$. Define
$\psi: (\Z_2^{t})^{d+1} \to \mU(\mM)$ by 
\[\psi(z_0,\ldots,z_{d}) \,=\, U_{0,z_0} \cdots U_{d,z_{d}}\;,\]
where for each $i\in\{0,\ldots,d\}$ and $z_i\in \F_q$, $U_{i,z_i}$ is the unitary defined in Claim~\ref{claim:z2-stab-2b} and we slightly abused notation to identify $z_i\in \Z_2^t$ with the unique $\tilde{z}_i\in \F_q$ such that $\kappa(\tilde{z}_i)=z_i$ . Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_2^{t(d+1)}$ on $\mU(\mA)$, with respect to the exhaustive presentation. To verify this first note that for any unitaries $V,W$, and any $i,i'$ we have that on average over $u$ and $j$,
\begin{align*}
\Es{\alpha,\alpha'\in \F_q} \big\| V U_{i,\alpha} U_{i',\alpha'} W^* - V U_{i',\alpha'} U_{i,\alpha}  W^*\big\|_\tau^2 \,=\, O\big(d^2 \sqrt{\eps}\big)\;,
\end{align*}
by Claim~\ref{claim:z2-stab-2b}, where the factor $d^2$ is because we require the relation to hold for all $i,i'$. Moreover, $U_{i,\alpha}U_{i,\alpha'}=U_{i,\alpha+\alpha'}$ by definition. Applying these relation $O(d^2)$ times gives
\begin{align*}
 \Es{z_0,\ldots,z_d\in\F_2^t}\Es{y_0,\ldots,y_d\in\F_2^t}\big\|\psi(z_0,\ldots,z_d)\psi(y_0,\ldots,y_d) -\psi(z_0+y_0,\ldots,z_d+y_d)\big\|_\tau^2 \,=\, O\big(d^4 \sqrt{\eps}\big)\;,
\end{align*}
as desired.
Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_{i,k}\}$ of order $2$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$, defining $V_i^z = \prod_{k=1}^t V_{i,k}^{z_k}$,
\begin{equation}\label{eq:z2-stab-3-1}
\Es{z_0,\ldots,z_{d}\in\F_2^t} \big\| \psi(z_0,\ldots,z_{d+1}) - w^* V_0^{z_0}\cdots V_{d}^{z_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
\end{equation}
Because $\{V_{i,z}\}$ are a representation of $\Z_2^{t(d+1)}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \Z_2^{t(d+1)}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$, 
\[ V_{i}^{z} \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\alpha_{i}\cdot z} Q_\alpha\;,\]
and  
\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\sum \alpha_{i}\cdot z_i} Q_\alpha\;.\]
Identifying $\alpha$ with an element of $\F_q^{d+1}$, and interpreting $z_i$ as an element of $\F_q$ as well,
 the preceding equation can be rewritten as
\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum \alpha_{i} z_i} Q_\alpha\;.\]

%($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in (\F_q)^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in (\F_q^{d+1}} (-1)^{\tr(\sum z_i\alpha_i)} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
\end{proof}

@@

\begin{claim}\label{claim:z2-stab-5}
Use the same notation as in Claim~\ref{claim:z2-stab-2b}. Let $u\in \F_q^m$, $\ell$ an axis-parallel line through $u$ and $v\in\F_q^m\cap \ell$. Let $(\alpha_{u,v,i})_{i=0,\ldots,d}$ be the interpolation coefficients~\eqref{eq:interp-coeff}. %Let $U_v = \sum_\beta \omega^\beta P^v_\beta$. 
Then 
\begin{equation}\label{eq:z2-stab-5-0}
\Es{u\in\F_q^m} \Es{\ell: u\in \ell} \Es{v\in \ell} \Es{\gamma\in\F_q} \Big\| U_{0,\gamma \alpha_{u,v,0}}\cdots U_{d,\gamma  \alpha_{u,v,d}} - U_{v,\gamma} \big\|_\tau^2 \,=\, 1-O\big(d\sqrt{\eps}\big)\;,
\end{equation}
where the expectation is over a uniformly random axis-parallel line that contains $u$, and a uniformly random $v\in\ell$. 
\end{claim}

\begin{proof}
Write $\alpha_i$ for $\alpha_{u,v,i}$. 
We observe that 
\begin{align*}
\Es{\gamma\in\F_q} \tau\big( U_{0,\gamma\alpha_{0}}\cdots U_{d,\gamma\alpha_{d}} U_{v,-\gamma} \big)
&=  \sum_{\beta_0,\ldots,\beta_d\in\F_q}\sum_{\beta\in\F_q} \Es{\gamma\in\F_q} (-1)^{\tr(\sum \gamma \alpha_i\beta_i)} (-1)^{\tr(-\gamma\beta)} \tau\big( P^{(0)}_{\beta_0} \cdots P^{(d)}_{\beta_d} P^v_\beta \big)\\
&= \sum_{\beta_0,\ldots,\beta_d\in\F_q}\sum_{\beta\in\F_q}\Es{\gamma\in\F_2^t} (-1)^{\gamma\cdot \kappa(\sum \alpha_i\beta_i-\beta)} \tau\big( P^{(0)}_{\beta_0} \cdots P^{(d)}_{\beta_d} P^v_\beta \big)\\
&=\Es{\gamma\in\F_2^t}  \tau\Big( \Big(\sum_{\beta_0\in \F_q} (-1)^{\gamma\cdot \kappa(\alpha_0\beta_0)} P^{(0)}_{\beta_0} \Big)\cdots\Big(\sum_{\beta\in \F_q} (-1)^{-\gamma\cdot \kappa(\beta)} P^{v}_{\beta} \Big)\Big)\\
&=\Es{\gamma\in\F_q}  \tau\Big( \Big(\sum_{\beta_0\in \F_q} (-1)^{\kappa( \gamma \alpha_0)\cdot\kappa(\beta_0)} P^{(0)}_{\beta_0} \Big)\cdots\Big(\sum_{\beta\in \F_q} (-1)^{\kappa(-\gamma)\cdot \kappa(\beta)} P^{v}_{\beta} \Big)\Big)\;.
\end{align*}
By repeated application of Claim~\ref{claim:z2-stab-2}, the last expression is within $O(d\sqrt{\eps})$ of 
\[ \Es{\gamma\in\F_q}  \tau\big( \phi(s_{u+ie_j,\kappa(\gamma \alpha_0)})\cdots \phi(s_{v,\kappa(-\gamma)}) \big)\;.\]
The latter expression is a random relation in $R^\ld_k$, and so, on average over $u,j$ and $v$ it is $1-O(\eps)$.
\end{proof}
